BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for Realistic BPMN Models

### 2024-07-31 main.tex
Reduce paper size

%% hf: enable header and footer.
\documentclass[
twocolumn, % TODO: has to be one col
% hf, % <-- Not sure if this should be enabled
]{ceurart}

@@

\textbf{First}, we benchmarked how our tool handles \textbf{BPMN models of growing size}.
We generated 500 synthetic BPMN models starting with five elements up to 4000.
The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (more details in~\cite{krauterInstantaneousComprehensibleFixable2024}).

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{images/model-size-benchmark}
	\caption{Analysis runtime for models of increasing size}
	\label{fig:model-size-benchmark}
\end{figure}

\autoref{fig:model-size-benchmark} shows that the BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models compared to 0.7 s up to 14 s in our previous tool~\cite{krauterFormalizationAnalysisBPMN2023}.
In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime observed in \autoref{fig:model-size-benchmark}.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{images/parallel-branches}
	\caption{Models with a growing number of parallel branches and branch length}
	\label{fig:parallel-branches-models}
\end{figure}

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.82\linewidth]{images/counter-example}
	\caption{\textit{Interactive} erroneous execution example shown in the BPMN Analyzer}
	\label{fig:counterexample}
\end{figure*}

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.82\linewidth]{images/quick-fix}
	\caption{Suggested \textit{quick fixes} in the BPMN Analyzer}
	\label{fig:quick-fixes}
\end{figure*}

>>>>

%% hf: enable header and footer.
\documentclass[
onecolumn, % TODO: has to be one col
% hf, % <-- Not sure if this should be enabled
]{ceurart}

@@

\textbf{First}, we benchmarked how our tool handles \textbf{BPMN models of growing size}.
We generated 500 synthetic BPMN models starting with five elements up to 4000.
The models repeatedly contain three activities and an exclusive/parallel block with two branches containing one activity per branch (see ~\cite{krauterInstantaneousComprehensibleFixable2024}).
The BPMN Analyzer spends from 1 ms up to 9 ms for the BPMN models~\cite{krauterInstantaneousComprehensibleFixable2024} compared to 0.7 s up to 14 s in our previous tool~\cite{krauterFormalizationAnalysisBPMN2023}.
In summary, the linear growth of the models leads to a linear growth in state space and, consequently, a linear growth in runtime.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.5\linewidth]{images/parallel-branches}
	\caption{Models with a growing number of parallel branches and branch length}
	\label{fig:parallel-branches-models}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.6\linewidth]{images/counter-example}
	\caption{\textit{Interactive} erroneous execution example shown in the BPMN Analyzer}
	\label{fig:counterexample}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=0.6\linewidth]{images/quick-fix}
	\caption{Suggested \textit{quick fixes} in the BPMN Analyzer}
	\label{fig:quick-fixes}
\end{figure}
